---
title: "Group 18 UCSB domestic grad enrollment"
author: "Patrick Pelegri-O'Day, Deanna Elliott"
date: "11/13/2021"
output: html_document
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(here)
library(tidyverse)
```

Read in data
```{r}
ucsb_grad <-
  read_csv(here("data", "ucsb_grad_data.csv"))
```

Plot domestic enrollment vs enrollment year

```{r}

ggplot(data = ucsb_grad,
       aes(x = year_abbr, y = domestic_enrollment, fill = ethnicity))+
  geom_col(position = "fill") +
  labs(x = "Year", y = " % Domestic Enrollment", fill = "Ethnicity",
       title = "UCSB Domestic Graduate Enrollment by Ethnicity") +
  theme_minimal()
```

**Figure 1. Percentage of graduate domestic enrollment by ethnicity.** This graph shows domestic enrollment in graduate programs at UCSB based on enrollment year and student ethnicity. White students represent 50-65% every year, followed distantly by Asian American, Latino, and Chicano students. American Indian/Alaskan students hold the lowest percent representation.